% Created 2019-06-27 木 15:54
% Intended LaTeX compiler: pdflatex
\documentclass{article}

\usepackage{authblk}
\usepackage{graphicx}
\usepackage{amsfonts}
\usepackage{booktabs}
\usepackage{framed}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{tabularx}

\newcolumntype{x}[1]{>{\centering\arraybackslash\hspace{0pt}}p{#1}}
\newcolumntype{y}[1]{>{\raggedright\arraybackslash\hspace{0pt}}p{#1}}


\date{} \title{Finding Shortest Reconfigurations Sequences of
  Independent Sets} \pagenumbering{gobble}

\author{Volker Turau}
\author{Christoph Weyer}
\affil{Institute of Telematics, Hamburg University of Technology\\ Hamburg, Germany\\ turau@tuhh.de}

\begin{document}
\maketitle

\section{Algorithm}
The problem at hand is a classical problem in graph theory: find a
path between two given vertices in an undirected graph such that the
sum of the weights of its constituent edges is minimized. Since in our
case all edge weights are equal to $1$ this is equivalent to finding
the path with fewest edges. There is a myriad of algorithms available
for this problem. The challenge in this case is that the graph
(a.k.a.\ the reconfiguration graph) as is only defined implicitly,
i.e., the vertices and edges are not explicitly given but rather
determined algorithmicly from the input. In addition this implicit
graph is rather large, too large to fit into the main memory of
current computers. This situation is very common in many search
problems. Hence, search algorithms such as A$^\ast$ are good
candidates to solve the given problem. The disadvantage of these
algorithms is that they keep all generated vertices in memory. For
example A$^\ast$ keeps two lists: {\em open} and {\em closed} vertices
and all vertices touched before finding a solution end up in one of
the two lists. Thus, for graphs with more than $10^{10}$ vertices this
requires at 100 GB to 1 T GB of RAM. This outstrips current
off-the-shelf hardware. Therefore memory-bounded heuristic searches
such as SMA$^\ast$ or IDA$^\ast$ are a better choice. We use Iterative
Deepening A$^\ast$ (IDA$^\ast$) and adapt it to our needs.

IDA$^\ast$ roughly works as follows: In each iteration it performs a
limited horizon depth-first search. The horizon is defined using a
heuristic estimate of the length of the path from the current vertex
to the target vertex. The horizon is the sum of the current distance
and the heuristic estimate. The horizon is increased at the end of
each iteration by the smallest value that exceed the last horizon.
There is a trade of between the quality of a heuristic and the
complexity of evaluating the heuristic. Since for large search
problems the heuristic is evaluated extremely often it is necessary to
choose a simple heuristic that can be preferably computed in constant
time. Since in our case the vertices of the implicit graph correspond
to independent sets of the input graph, we used the following simple
heuristic to estimate the distance from the current independent set
$C$ to the target independent set $T$: $h(C) :=|C\setminus T|$, i.e.,
the node of vertices that are not yet in the target set. This
heuristic is easy to compute. Also it is {\em consistent}, this
guarantees that IDA$^\ast$ finds the shortest path.

The downside of informed search algorithms is that if there is no
solution -- i.e., start and target vertex are in different connected
components -- they have to access every vertex of the connected
component of the graph that contains the start vertex at least once.
This problem is aggravated by the fact, that IDA$^\ast$ increases its
horizon gradually. So in case no solution exists the number of
operations roughly grows exponentially with the diameter of the graph.
Thus, in this case a simpler approach is required. We have used a
variant of breadth-first search (BFS) for this purpose, that does not
require to explicitly store the visited vertices and evaluates no
heuristic.

Since it is not known upfront whether a solution exits we have decided
to use both approaches concurrently. After initializing the data
structures from the input files we launch two threads. The first one
executes our version of the breadth-first search while the second
executes our variant of IDA$^\ast$. Whichever thread first finds a
shortest path between start and target vertex or finds out that these
vertices lie in in different connected components of the implicit
graph ends the program and outputs a solution.

The main challenge in solving shortest path problems for large graphs
is to use a data structure that allows to quickly determine the
neighbors of a vertex in the implicit graph and to quickly evaluate
the heuristic. Since vertices in the implicit graph correspond to
independent sets we used an adjacency matrix to represent the input
graph. Each row of this matrix consists of $n$ bits ($n$ is the number
of vertices of the input graph). Thus, a row is represent as
$\lceil n/64\rceil$ words of size $64$. The reason for this choice is
that current computers have a word size of 64 bits. A vertex of the
implicit graph -- an independent set of the input graph -- is thus
also represented by a bit field consisting of $\lceil n/64\rceil$
words. Thus, given that $X$ is an independent set, to check whether
$X\setminus \{x\} \cup \{y\}$ is also independent can be decided by at
most $\lceil n/64\rceil$ XOR operations. We can update independent
sets in constant time. Similarly, we can for a given independent set
compute its neighboring independent sets in time $O(n)$ time.
Moreover, very efficient low level functions for this type of
representation are available, e.g.,  {\em \_\_builtin\_ffsll} for
computing the index of the first bit set. At no time we have to
iterate over the neighborhood of a vertex.

To cope with the large number of vertices we used different techniques.
In BFS we represented the vertices of every layer in a separate AVL tree.
We maintain at any time only the top two layers of the BFS tree. The
predecessor relation is maintained with reference counters. At the
completion of each layer, lower layers are thinned out by recursively
removing vertices with no successor, i.e., reference counter 0. Vertices in
the AVL trees correspond to independent sets. In order to speed up the
search in such trees we additionally stored a 64 Bit hash value with
each independent set. Thus, first we compared the hash values and only
if these coincided we needed to explicitly compare the independent
sets. Therefore, in most cases a comparison only required one
operation.

We implemented a variant of IDA$^\ast$. To speed up this algorithm we
maintained a compact history between individual iterations. This
history includes information at what distance from the start vertex a
vertex appeared. If it reappears at the same or a larger distance it
can be skipped. At the beginning of a new iteration the history was
{\em lifted}, i.e., the distance of each vertex is incremented by 1,
so that we search beyond the previous horizon. This helps to
considerably reduce the number of vertices that had to be revisited.
Also, since this history is not required for the algorithm to work
correctly, we can at any time close the history to limit the usage of
RAM. The history is implemented as hash table using open addressing,
in particular we used linear probing, the hash function {\em
  MurmurHash2} yielding hash values of size 64 bit, and a load factor
of $5/8$. We also designed the data structures such as AVL trees in a
way that allows to efficiently allocate and deallocate the required
memory.

The algorithm is to a large degree a general search algorithm. It can
use the TS (token sliding) or the TJ (token jumping) model. Some of
the problem specific aspects are as follows.
\begin{itemize}
\item The estimate function $h(C)$, it can be computed in constant
  time given the value of the previous state.
\item The successors of a vertex in the search graph can be found very
  efficiently by maintaining for each node the number of neighbors
  that are in the current independent set. There are only two cases.
  If a node has no such neighbor, then every token can be placed on
  it. If it has a single such neighbor then the token of this neighbor
  can be placed on it.
\item Representing the graph as a bitset allowed to implement many
  basic graph operations with logical operators such as {\em and, or},
  and {\em xor} on words of length 64 bit.
\end{itemize}



A simple extension of the algorithm would be to run two more threads
that start to search from the target independent set. For the graphs
in the benchmark that did not bring any benefit, because they seem to
be {\em symmetric} with respect to start and target. We do not know
whether this property holds in general, properly not.

\section{Implementation Details}
The algorithm is implemented in the programming language C, using c99.
As a compiler we used {\em clang} with options {\em -Ofast
  -march=native -mtune=native}. The source code consists of seven
modules, in total about 50 KiB of code. The threads are implemented
using {\em pthread}. We do not use any third party software.

\section{Computation Environment}

We run our benchmarks on the following configuration. We used an Ubuntu 20.04
virtual machine with 4 logical CPUs and 60\,GiB RAM. Our program uses only 2
CPUs. The server uses Proxmox as virtualization environment. The server has an
AMD Ryzen9 3900X CPU with 12 cores at 3.80\,GHz. For storage we use NVMe SSDs.

\section{Solutions}

In the following tables we summarize the outcome of our program. The
corresponding output files can be found in die \texttt{solutions} directory.
The column solution specifies if no path can be found or the number of steps
for the shortest path. The time column is the measured elapsed time from the
Unix tool \texttt{time} as \texttt{HH:MM:SS.mm}. If a program runs longer than
one hour no milliseconds are given.

When we found no solution for the given problem due to time constraints a ---
is shown.

\begin{table}[t]\footnotesize\center
  \begin{tabular}{y{3.6cm}x{1cm}x{1.5cm}x{1.5cm}y{1.5cm}}
    \multicolumn{1}{c}{\textbf{Dat File}} &
    \multicolumn{1}{c}{\textbf{n}} &
    \multicolumn{1}{c}{\textbf{m}} &
    \multicolumn{1}{c}{\textbf{Solution}} &
    \multicolumn{1}{c}{\textbf{Time}} \\
    \verb|grid004x004_01.dat|  & 16 & 24 & No & 00:00:00.07 \\
    \verb|grid004x004_02.dat|  & 16 & 24 & No & 00:00:00.05 \\
    \verb|grid004x004_03.dat|  & 16 & 24 &  7 & 00:00:00.05 \\
    \verb|grid004x004_04.dat|  & 16 & 24 &  8 & 00:00:00.05 \\
    \verb|grid004x004_05.dat|  & 16 & 24 & No & 00:00:00.07 \\
    \verb|hc-power-11_01.dat|  & 21 & 28 & 21 & 00:00:00.06 \\
    \verb|hc-power-12_01.dat|  & 36 & 51 & 69 & 00:00:00.05 \\
    \verb|hc-square-01_01.dat| & 14 & 18 & 12 & 00:00:00.05 \\
    \verb|hc-square-02_01.dat| & 24 & 33 & 30 & 00:00:00.05 \\
    \verb|hc-toyno-01_01.dat|  &  6 &  9 & No & 00:00:00.05 \\
    \verb|hc-toyyes-01_01.dat| &  7 &  7 &  3 & 00:00:00.05 \\
  \end{tabular}
  \caption{Solutions for first benchmark}
\end{table}

\begin{table}\footnotesize\center
  \begin{tabular}{y{3.6cm}x{1cm}x{1.5cm}x{1.5cm}y{1.5cm}}
    \multicolumn{1}{c}{\textbf{Dat File}} &
    \multicolumn{1}{c}{\textbf{n}} &
    \multicolumn{1}{c}{\textbf{m}} &
    \multicolumn{1}{c}{\textbf{Solution}} &
    \multicolumn{1}{c}{\textbf{Time}} \\
    \verb|grid010x010_01_6141.dat| &   100 &   180 &  No & 00:00:00.05 \\
    \verb|grid010x010_02_0495.dat| &   100 &   180 &  No & 00:00:00.05 \\
    \verb|grid010x010_03_6844.dat| &   100 &   180 &  No & 00:00:00.05 \\
    \verb|grid010x010_04_4957.dat| &   100 &   180 &  No & 00:00:00.08 \\
    \verb|grid020x020_01_9275.dat| &   400 &   760 &  No & 00:00:01.40 \\
    \verb|grid020x020_02_7550.dat| &   400 &   760 &  No & 00:00:00.07 \\
    \verb|grid020x020_03_3902.dat| &   400 &   760 &  No & 00:00:01.44 \\
    \verb|grid020x020_04_3283.dat| &   400 &   760 &  No & 00:00:00.05 \\
    \verb|grid030x030_01_6931.dat| &   900 &  1740 &  No & 00:00:00.05 \\
    \verb|grid030x030_02_7112.dat| &   900 &  1740 &  No & 00:00:21.81 \\
    \verb|grid030x030_03_4248.dat| &   900 &  1740 &  No & 00:00:00.05 \\
    \verb|grid030x030_04_2988.dat| &   900 &  1740 &  No & 00:00:22.17 \\
    \verb|grid040x040_01_6703.dat| &  1600 &  3120 &  No & 00:00:00.13 \\
    \verb|grid040x040_02_3552.dat| &  1600 &  3120 &  No & 00:00:00.09 \\
    \verb|grid040x040_03_0746.dat| &  1600 &  3120 &  No & 00:02:29.34 \\
    \verb|grid040x040_04_3680.dat| &  1600 &  3120 &  No & 00:02:35.90 \\
    \verb|grid050x050_01_8271.dat| &  2500 &  4900 &  No & 00:00:00.31 \\
    \verb|grid050x050_02_8314.dat| &  2500 &  4900 &  No & 00:14:18.34 \\
    \verb|grid050x050_03_4298.dat| &  2500 &  4900 &  No & 00:00:00.29 \\
    \verb|grid050x050_04_8232.dat| &  2500 &  4900 &  No & 00:14:16.52 \\
    \verb|grid060x060_01_5912.dat| &  3600 &  7080 &  No & 00:00:00.62 \\
    \verb|grid060x060_02_4571.dat| &  3600 &  7080 &  No & 00:57:59.71 \\
    \verb|grid060x060_03_2183.dat| &  3600 &  7080 &  No & 00:57:30.17 \\
    \verb|grid060x060_04_3263.dat| &  3600 &  7080 &  No & 00:00:00.63 \\
    \verb|grid070x070_01_6558.dat| &  4900 &  9660 &  No & 00:00:01.41 \\
    \verb|grid070x070_02_7903.dat| &  4900 &  9660 &  No & 02:43:26 \\
    \verb|grid070x070_03_4857.dat| &  4900 &  9660 &  No & 02:45:27 \\
    \verb|grid070x070_04_3525.dat| &  4900 &  9660 &  No & 00:00:01.35 \\
    \verb|grid080x080_01_9321.dat| &  6400 & 12640 &  No & 00:00:02.76 \\
    \verb|grid080x080_02_8623.dat| &  6400 & 12640 &  No & 06:50:57 \\
    \verb|grid080x080_03_8653.dat| &  6400 & 12640 &  No & 00:00:02.77 \\
    \verb|grid080x080_04_8592.dat| &  6400 & 12640 &  No & 06:55:10 \\
    \verb|grid090x090_01_0710.dat| &  8100 & 16020 &  No & 18:55:31 \\
    \verb|grid090x090_02_9631.dat| &  8100 & 16020 &  No & 00:00:07.58 \\
    \verb|grid090x090_03_8778.dat| &  8100 & 16020 &  No & 19:37:18 \\
    \verb|grid090x090_04_4969.dat| &  8100 & 16020 &  No & 00:00:07.56 \\
    \verb|grid100x100_01_9072.dat| & 10000 & 19800 &  No & 38:47:16 \\
    \verb|grid100x100_02_7191.dat| & 10000 & 19800 &  No & 00:00:11.73 \\
    \verb|grid100x100_03_4887.dat| & 10000 & 19800 &  No & 39:08:22 \\
    \verb|grid100x100_04_0664.dat| & 10000 & 19800 &  No & 00:00:11.96 \\
    \verb|grid200x200_01_8265.dat| & 40000 & 79600 & --- & --- \\
    \verb|grid200x200_02_2458.dat| & 40000 & 79600 &  No & 00:11:13.24 \\
    \verb|grid200x200_03_0743.dat| & 40000 & 79600 &  No & 00:11:09.19 \\
    \verb|grid200x200_04_2816.dat| & 40000 & 79600 & --- & --- \\
  \end{tabular}
  \caption{Solutions for grid benchmarks}
\end{table}

\begin{table}\footnotesize\center
  \begin{tabular}{y{3.6cm}x{1cm}x{1.5cm}x{1.5cm}y{1.5cm}}
    \multicolumn{1}{c}{\textbf{Dat File}} &
    \multicolumn{1}{c}{\textbf{n}} &
    \multicolumn{1}{c}{\textbf{m}} &
    \multicolumn{1}{c}{\textbf{Solution}} &
    \multicolumn{1}{c}{\textbf{Time}} \\
    \verb|queen008x008_01_4136.dat| &    64 &      728 &   9 & 00:00:00.13 \\
    \verb|queen008x008_02_8804.dat| &    64 &      728 &  11 & 00:00:00.05 \\
    \verb|queen008x008_03_8723.dat| &    64 &      728 &  11 & 00:00:00.05 \\
    \verb|queen008x008_04_4441.dat| &    64 &      728 &  12 & 00:00:00.05 \\
    \verb|queen010x010_01_0612.dat| &   100 &     1470 &  10 & 00:00:00.05 \\
    \verb|queen010x010_02_5832.dat| &   100 &     1470 &  11 & 00:00:00.05 \\
    \verb|queen010x010_03_7635.dat| &   100 &     1470 &  13 & 00:00:00.05 \\
    \verb|queen010x010_04_2943.dat| &   100 &     1470 &  14 & 00:00:00.05 \\
    \verb|queen020x020_01_7075.dat| &   400 &    12540 &  24 & 00:00:00.57 \\
    \verb|queen020x020_02_4815.dat| &   400 &    12540 &  22 & 00:00:00.31 \\
    \verb|queen020x020_03_8667.dat| &   400 &    12540 &  21 & 00:00:00.38 \\
    \verb|queen020x020_04_0961.dat| &   400 &    12540 &  18 & 00:00:00.25 \\
    \verb|queen030x030_01_3761.dat| &   900 &    43210 &  15 & 00:00:00.13 \\
    \verb|queen030x030_02_4963.dat| &   900 &    43210 &  26 & 00:00:03.61 \\
    \verb|queen030x030_03_7394.dat| &   900 &    43210 &  26 & 00:00:02.41 \\
    \verb|queen030x030_04_9144.dat| &   900 &    43210 &  24 & 00:00:00.66 \\
    \verb|queen040x040_01_6291.dat| &  1600 &   103480 &  13 & 00:00:00.08 \\
    \verb|queen040x040_02_9487.dat| &  1600 &   103480 &  14 & 00:00:00.14 \\
    \verb|queen040x040_03_7037.dat| &  1600 &   103480 &  14 & 00:00:00.12 \\
    \verb|queen040x040_04_8369.dat| &  1600 &   103480 &  17 & 00:00:00.14 \\
    \verb|queen050x050_01_6006.dat| &  2500 &   203350 &  13 & 00:00:00.12 \\
    \verb|queen050x050_02_6166.dat| &  2500 &   203350 &  16 & 00:00:00.12 \\
    \verb|queen050x050_03_0562.dat| &  2500 &   203350 &   6 & 00:00:00.08 \\
    \verb|queen050x050_04_9047.dat| &  2500 &   203350 &  12 & 00:00:00.10 \\
    \verb|queen060x060_01_8336.dat| &  3600 &   352820 &   5 & 00:00:00.12 \\
    \verb|queen060x060_02_6710.dat| &  3600 &   352820 &   9 & 00:00:00.12 \\
    \verb|queen060x060_03_1394.dat| &  3600 &   352820 &   9 & 00:00:00.10 \\
    \verb|queen060x060_04_3799.dat| &  3600 &   352820 &   9 & 00:00:00.11 \\
    \verb|queen070x070_01_1828.dat| &  4900 &   561890 &  38 & 04:21:08 \\
    \verb|queen070x070_02_8683.dat| &  4900 &   561890 &  40 & 00:38:16.40 \\
    \verb|queen070x070_03_1545.dat| &  4900 &   561890 &  34 & 00:01:23.21 \\
    \verb|queen070x070_04_7426.dat| &  4900 &   561890 &  33 & 00:01:06.70 \\
    \verb|queen080x080_01_0297.dat| &  6400 &   840560 &  25 & 00:00:10.44 \\
    \verb|queen080x080_02_2368.dat| &  6400 &   840560 &  31 & 00:05:34.91 \\
    \verb|queen080x080_03_0355.dat| &  6400 &   840560 & --- & --- \\
    \verb|queen080x080_04_4954.dat| &  6400 &   840560 &  36 & 00:10:46.40 \\
    \verb|queen090x090_01_8978.dat| &  8100 &  1198830 & --- & --- \\
    \verb|queen090x090_02_0808.dat| &  8100 &  1198830 &  41 & 02:06:41 \\
    \verb|queen090x090_03_9570.dat| &  8100 &  1198830 & --- & --- \\
    \verb|queen090x090_04_1188.dat| &  8100 &  1198830 &  38 & 00:05:02.33 \\
    \verb|queen100x100_01_3955.dat| & 10000 &  1646700 & --- & --- \\
    \verb|queen100x100_02_1699.dat| & 10000 &  1646700 &   6 & 00:00:00.38 \\
    \verb|queen100x100_03_6670.dat| & 10000 &  1646700 & --- & --- \\
    \verb|queen100x100_04_0618.dat| & 10000 &  1646700 & --- & --- \\
    \verb|queen200x200_01_0761.dat| & 40000 & 13253400 &   4 & 00:00:02.09 \\
    \verb|queen200x200_02_3057.dat| & 40000 & 13253400 &  29 & 00:00:10.10 \\
    \verb|queen200x200_03_0327.dat| & 40000 & 13253400 &  29 & 00:00:10.08 \\
    \verb|queen200x200_04_4796.dat| & 40000 & 13253400 &  27 & 00:00:03.06 \\
  \end{tabular}
  \caption{Solutions for queen benchmarks}
\end{table}

\begin{table}\footnotesize\center
  \begin{tabular}{y{3.6cm}x{1cm}x{1.5cm}x{1.5cm}y{1.5cm}}
    \multicolumn{1}{c}{\textbf{Dat File}} &
    \multicolumn{1}{c}{\textbf{n}} &
    \multicolumn{1}{c}{\textbf{m}} &
    \multicolumn{1}{c}{\textbf{Solution}} &
    \multicolumn{1}{c}{\textbf{Time}} \\
    \verb|hc-square-004-002_01.dat| &  44 &  63 &   90 & 00:00:00.05 \\
    \verb|hc-square-005-002_01.dat| &  54 &  78 &  132 & 00:00:00.05 \\
    \verb|hc-square-006-002_01.dat| &  64 &  93 &  182 & 00:00:00.07 \\
    \verb|hc-square-007-002_01.dat| &  74 & 108 &  240 & 00:00:00.49 \\
    \verb|hc-square-008-002_01.dat| &  84 & 123 &  306 & 00:00:03.39 \\
    \verb|hc-square-009-002_01.dat| &  94 & 138 &  380 & 00:00:25.28 \\
    \verb|hc-square-010-002_01.dat| & 104 & 153 &  462 & 00:03:04.50 \\
    \verb|hc-square-011-002_01.dat| & 114 & 168 &  552 & 00:24:20.14 \\
    \verb|hc-square-012-002_01.dat| & 124 & 183 &  650 & 03:06:18 \\
    \verb|hc-square-013-002_01.dat| & 134 & 198 &  756 & 23:08:27 \\
    \verb|hc-square-014-002_01.dat| & 144 & 213 &  --- & --- \\
    \verb|hc-square-015-002_01.dat| & 154 & 228 &  --- & --- \\
    \verb|hc-square-016-002_01.dat| & 164 & 243 &  --- & --- \\
    \verb|hc-square-017-002_01.dat| & 174 & 258 &  --- & --- \\
    \verb|hc-square-018-002_01.dat| & 184 & 273 &  --- & --- \\
    \verb|hc-square-019-002_01.dat| & 194 & 288 &  --- & --- \\
    \verb|hc-square-020-002_01.dat| & 204 & 303 &  --- & --- \\
  \end{tabular}
  \caption{Solutions for square benchmarks}
\end{table}

\begin{table}\footnotesize\center
  \begin{tabular}{y{3.6cm}x{1cm}x{1.5cm}x{1.5cm}y{1.5cm}}
    \multicolumn{1}{c}{\textbf{Dat File}} &
    \multicolumn{1}{c}{\textbf{n}} &
    \multicolumn{1}{c}{\textbf{m}} &
    \multicolumn{1}{c}{\textbf{Solution}} &
    \multicolumn{1}{c}{\textbf{Time}} \\
    \verb|hc-power-004-002_01.dat| &  64 &  95 &   359 & 00:00:00.07 \\
    \verb|hc-power-005-002_01.dat| &  79 & 118 &   779 & 00:00:00.21 \\
    \verb|hc-power-006-002_01.dat| &  94 & 141 &  1631 & 00:00:02.24 \\
    \verb|hc-power-007-002_01.dat| & 109 & 164 &  3347 & 00:00:25.03 \\
    \verb|hc-power-008-002_01.dat| & 124 & 187 &  6791 & 00:04:39.50 \\
    \verb|hc-power-009-002_01.dat| & 139 & 210 & 13691 & 00:57:44.86 \\
    \verb|hc-power-010-002_01.dat| & 154 & 233 & 27503 & 11:00:38 \\
    \verb|hc-power-011-002_01.dat| & 169 & 256 &  ---  & --- \\
    \verb|hc-power-012-002_01.dat| & 184 & 279 &  ---  & --- \\
    \verb|hc-power-013-002_01.dat| & 199 & 302 &  ---  & --- \\
    \verb|hc-power-014-002_01.dat| & 214 & 325 &  ---  & --- \\
    \verb|hc-power-015-002_01.dat| & 229 & 348 &  ---  & --- \\
    \verb|hc-power-016-002_01.dat| & 244 & 371 &  ---  & --- \\
    \verb|hc-power-017-002_01.dat| & 259 & 394 &  ---  & --- \\
    \verb|hc-power-018-002_01.dat| & 274 & 417 &  ---  & --- \\
    \verb|hc-power-019-002_01.dat| & 289 & 440 &  ---  & --- \\
    \verb|hc-power-020-002_01.dat| & 304 & 463 &  ---  & --- \\
  \end{tabular}
  \caption{Solutions for power benchmarks}
\end{table}

\begin{table}\footnotesize\center
  \begin{tabular}{y{3.6cm}x{1cm}x{1.5cm}x{1.5cm}y{1.5cm}}
    \multicolumn{1}{c}{\textbf{Dat File}} &
    \multicolumn{1}{c}{\textbf{n}} &
    \multicolumn{1}{c}{\textbf{m}} &
    \multicolumn{1}{c}{\textbf{Solution}} &
    \multicolumn{1}{c}{\textbf{Time}} \\
    \verb|sp001_01.dat| &  13 &   66 &    11 & 00:00:00.05 \\
    \verb|sp002_01.dat| &  26 &  150 &    33 & 00:00:00.05 \\
    \verb|sp003_01.dat| &  39 &  234 &    77 & 00:00:00.05 \\
    \verb|sp004_01.dat| &  52 &  318 &   165 & 00:00:00.05 \\
    \verb|sp005_01.dat| &  65 &  402 &   341 & 00:00:00.05 \\
    \verb|sp006_01.dat| &  78 &  486 &   693 & 00:00:00.20 \\
    \verb|sp007_01.dat| &  91 &  570 &  1397 & 00:00:01.77 \\
    \verb|sp008_01.dat| & 104 &  654 &  2805 & 00:00:15.77 \\
    \verb|sp009_01.dat| & 117 &  738 &  5621 & 00:02:27.31 \\
    \verb|sp010_01.dat| & 130 &  822 & 11253 & 00:24:02.35 \\
    \verb|sp011_01.dat| & 143 &  906 & 22517 & 04:04:29 \\
    \verb|sp012_01.dat| & 156 &  990 & 45045 & 40:45:33 \\
    \verb|sp013_01.dat| & 169 & 1074 &  ---  & --- \\
    \verb|sp014_01.dat| & 182 & 1158 &  ---  & --- \\
    \verb|sp015_01.dat| & 195 & 1242 &  ---  & --- \\
    \verb|sp016_01.dat| & 208 & 1326 &  ---  & --- \\
    \verb|sp017_01.dat| & 221 & 1410 &  ---  & --- \\
    \verb|sp018_01.dat| & 234 & 1494 &  ---  & --- \\
    \verb|sp019_01.dat| & 247 & 1578 &  ---  & --- \\
    \verb|sp020_01.dat| & 260 & 1662 &  ---  & --- \\
    \verb|sp021_01.dat| & 273 & 1746 &  ---  & --- \\
    \verb|sp022_01.dat| & 286 & 1830 &  ---  & --- \\
    \verb|sp023_01.dat| & 299 & 1914 &  ---  & --- \\
    \verb|sp024_01.dat| & 312 & 1998 &  ---  & --- \\
    \verb|sp025_01.dat| & 325 & 2082 &  ---  & --- \\
    \verb|sp026_01.dat| & 338 & 2166 &  ---  & --- \\
    \verb|sp027_01.dat| & 351 & 2250 &  ---  & --- \\
    \verb|sp028_01.dat| & 364 & 2334 &  ---  & --- \\
    \verb|sp029_01.dat| & 377 & 2418 &  ---  & --- \\
    \verb|sp030_01.dat| & 390 & 2502 &  ---  & --- \\
  \end{tabular}
  \caption{Solutions for SP benchmarks}
\end{table}

\begin{table}\footnotesize\center
  \begin{tabular}{y{3.6cm}x{1cm}x{1.5cm}x{1.5cm}y{1.5cm}}
    \multicolumn{1}{c}{\textbf{Dat File}} &
    \multicolumn{1}{c}{\textbf{n}} &
    \multicolumn{1}{c}{\textbf{m}} &
    \multicolumn{1}{c}{\textbf{Solution}} &
    \multicolumn{1}{c}{\textbf{Time}} \\
    \verb|1-FullIns_3_01.dat| & 30 & 100 & 1 & 00:00:00.06 \\
    \verb|1-FullIns_3_02.dat| & 30 & 100 & 3 & 00:00:00.06 \\
    \verb|1-FullIns_4_01.dat| & 93 & 593 & 1 & 00:00:00.05 \\
    \verb|1-FullIns_4_02.dat| & 93 & 593 & 1 & 00:00:00.05 \\
    \verb|1-FullIns_5_01.dat| & 282 & 3247 & 1 & 00:00:00.07 \\
    \verb|1-FullIns_5_02.dat| & 282 & 3247 & 1 & 00:00:00.06 \\
    \verb|1-Insertions_4_01.dat| & 67 & 232 & 3 & 00:00:00.05 \\
    \verb|1-Insertions_4_02.dat| & 67 & 232 & 2 & 00:00:00.05 \\
    \verb|1-Insertions_5_01.dat| & 202 & 1227 & 2 & 00:00:00.06 \\
    \verb|1-Insertions_5_02.dat| & 202 & 1227 & 2 & 00:00:00.05 \\
    \verb|1-Insertions_6_01.dat| & 607 & 6337 & 1 & 00:00:00.07 \\
    \verb|1-Insertions_6_02.dat| & 607 & 6337 & 3 & 00:00:00.05 \\
    \verb|2-FullIns_3_01.dat| & 52 & 201 & 2 & 00:00:00.05 \\
    \verb|2-FullIns_3_02.dat| & 52 & 201 & 2 & 00:00:00.05 \\
    \verb|2-FullIns_4_01.dat| & 212 & 1621 & 1 & 00:00:00.05 \\
    \verb|2-FullIns_4_02.dat| & 212 & 1621 & 1 & 00:00:00.05 \\
    \verb|2-FullIns_5_01.dat| & 852 & 12201 & 1 & 00:00:00.06 \\
    \verb|2-FullIns_5_02.dat| & 852 & 12201 & 1 & 00:00:00.05 \\
    \verb|2-Insertions_3_01.dat| & 37 & 72 & 3 & 00:00:00.06 \\
    \verb|2-Insertions_3_02.dat| & 37 & 72 & 2 & 00:00:00.05 \\
    \verb|2-Insertions_4_01.dat| & 149 & 541 & 1 & 00:00:00.05 \\
    \verb|2-Insertions_4_02.dat| & 149 & 541 & 1 & 00:00:00.05 \\
    \verb|2-Insertions_5_01.dat| & 597 & 3936 & 1 & 00:00:00.06 \\
    \verb|2-Insertions_5_02.dat| & 597 & 3936 & 1 & 00:00:00.05 \\
    \verb|3-FullIns_3_01.dat| & 80 & 346 & 2 & 00:00:00.05 \\
    \verb|3-FullIns_3_02.dat| & 80 & 346 & 4 & 00:00:00.06 \\
    \verb|3-FullIns_4_01.dat| & 405 & 3524 & 2 & 00:00:00.05 \\
    \verb|3-FullIns_4_02.dat| & 405 & 3524 & 3 & 00:00:00.05 \\
    \verb|3-FullIns_5_01.dat| & 2030 & 33751 & 1 & 00:00:00.06 \\
    \verb|3-FullIns_5_02.dat| & 2030 & 33751 & 5 & 00:00:00.06 \\
    \verb|3-Insertions_3_01.dat| & 56 & 110 & 4 & 00:00:00.05 \\
    \verb|3-Insertions_3_02.dat| & 56 & 110 & 2 & 00:00:00.05 \\
    \verb|3-Insertions_4_01.dat| & 281 & 1046 & 2 & 00:00:00.05 \\
    \verb|3-Insertions_4_02.dat| & 281 & 1046 & 5 & 00:00:00.05 \\
    \verb|3-Insertions_5_01.dat| & 1406 & 9695 & 1 & 00:00:00.08 \\
    \verb|3-Insertions_5_02.dat| & 1406 & 9695 & 1 & 00:00:00.05 \\
    \verb|4-FullIns_3_01.dat| & 114 & 541 & 1 & 00:00:00.05 \\
    \verb|4-FullIns_3_02.dat| & 114 & 541 & 1 & 00:00:00.05 \\
    \verb|4-FullIns_4_01.dat| & 690 & 6650 & 1 & 00:00:00.05 \\
    \verb|4-FullIns_4_02.dat| & 690 & 6650 & 2 & 00:00:00.05 \\
    \verb|4-FullIns_5_01.dat| & 4146 & 77305 & 1 & 00:00:00.07 \\
    \verb|4-FullIns_5_02.dat| & 4146 & 77305 & 1 & 00:00:00.07 \\
    \verb|4-Insertions_3_01.dat| & 79 & 156 & 1 & 00:00:00.05 \\
    \verb|4-Insertions_3_02.dat| & 79 & 156 & 3 & 00:00:00.05 \\
    \verb|4-Insertions_4_01.dat| & 475 & 1795 & 1 & 00:00:00.05 \\
    \verb|4-Insertions_4_02.dat| & 475 & 1795 & 1 & 00:00:00.05 \\
    \verb|5-FullIns_3_01.dat| & 154 & 792 & 1 & 00:00:00.05 \\
    \verb|5-FullIns_3_02.dat| & 154 & 792 & 5 & 00:00:00.05 \\
    \verb|5-FullIns_4_01.dat| & 1085 & 11395 & 1 & 00:00:00.07 \\
    \verb|5-FullIns_4_02.dat| & 1085 & 11395 & 6 & 00:00:00.05 \\
  \end{tabular}
  \caption{Solutions for color benchmarks (part 1)}
\end{table}
\begin{table}\footnotesize\center
  \begin{tabular}{y{3.6cm}x{1cm}x{1.5cm}x{1.5cm}y{1.5cm}}
    \multicolumn{1}{c}{\textbf{Dat File}} &
    \multicolumn{1}{c}{\textbf{n}} &
    \multicolumn{1}{c}{\textbf{m}} &
    \multicolumn{1}{c}{\textbf{Solution}} &
    \multicolumn{1}{c}{\textbf{Time}} \\
    \verb|DSJC1000.1_01.dat| & 1000 & 49629 & 1 & 00:00:00.06 \\
    \verb|DSJC1000.1_02.dat| & 1000 & 49629 & 3 & 00:00:00.06 \\
    \verb|DSJC1000.5_01.dat| & 1000 & 249826 & 6 & 00:00:00.10 \\
    \verb|DSJC1000.5_02.dat| & 1000 & 249826 & 2 & 00:00:00.08 \\
    \verb|DSJC1000.9_01.dat| & 1000 & 449449 & 2 & 00:00:00.11 \\
    \verb|DSJC1000.9_02.dat| & 1000 & 449449 & 2 & 00:00:00.11 \\
    \verb|DSJC125.1_01.dat| & 125 & 736 & 3 & 00:00:00.06 \\
    \verb|DSJC125.1_02.dat| & 125 & 736 & 5 & 00:00:00.05 \\
    \verb|DSJC125.5_01.dat| & 125 & 3891 & 4 & 00:00:00.06 \\
    \verb|DSJC125.5_02.dat| & 125 & 3891 & 2 & 00:00:00.05 \\
    \verb|DSJC125.9_01.dat| & 125 & 6961 & 1 & 00:00:00.05 \\
    \verb|DSJC125.9_02.dat| & 125 & 6961 & 8 & 00:00:00.05 \\
    \verb|DSJC250.1_01.dat| & 250 & 3218 & 1 & 00:00:00.05 \\
    \verb|DSJC250.1_02.dat| & 250 & 3218 & 1 & 00:00:00.05 \\
    \verb|DSJC250.5_01.dat| & 250 & 15668 & 1 & 00:00:00.05 \\
    \verb|DSJC250.5_02.dat| & 250 & 15668 & 5 & 00:00:00.05 \\
    \verb|DSJC250.9_01.dat| & 250 & 27897 & 5 & 00:00:00.22 \\
    \verb|DSJC250.9_02.dat| & 250 & 27897 & 5 & 00:00:00.05 \\
    \verb|DSJC500.1_01.dat| & 500 & 12458 & 3 & 00:00:00.05 \\
    \verb|DSJC500.1_02.dat| & 500 & 12458 & 6 & 00:00:00.05 \\
    \verb|DSJC500.5_01.dat| & 500 & 62624 & 1 & 00:00:00.07 \\
    \verb|DSJC500.5_02.dat| & 500 & 62624 & 1 & 00:00:00.06 \\
    \verb|DSJC500.9_01.dat| & 500 & 112437 & 6 & 00:00:00.08 \\
    \verb|DSJC500.9_02.dat| & 500 & 112437 & 9 & 00:00:00.06 \\
    \verb|DSJR500.1_01.dat| & 500 & 3555 & 8 & 00:00:00.05 \\
    \verb|DSJR500.1_02.dat| & 500 & 3555 & 13 & 00:00:00.05 \\
    \verb|DSJR500.1c_01.dat| & 500 & 121275 & 1 & 00:00:00.10 \\
    \verb|DSJR500.1c_02.dat| & 500 & 121275 & 4 & 00:00:00.06 \\
    \verb|DSJR500.5_01.dat| & 500 & 58862 & 2 & 00:00:00.06 \\
    \verb|DSJR500.5_02.dat| & 500 & 58862 & 6 & 00:00:00.07 \\
    \verb|anna_01.dat| & 138 & 493 & 5 & 00:00:00.05 \\
    \verb|anna_02.dat| & 138 & 493 & 13 & 00:00:00.05 \\
    \verb|ash331GPIA_01.dat| & 662 & 4181 & 1 & 00:00:00.05 \\
    \verb|ash331GPIA_02.dat| & 662 & 4181 & 1 & 00:00:00.06 \\
    \verb|ash608GPIA_01.dat| & 1216 & 7844 & 1 & 00:00:00.05 \\
    \verb|ash608GPIA_02.dat| & 1216 & 7844 & 1 & 00:00:00.05 \\
    \verb|ash958GPIA_01.dat| & 1916 & 12506 & 1 & 00:00:00.08 \\
    \verb|ash958GPIA_02.dat| & 1916 & 12506 & 1 & 00:00:00.06 \\
    \verb|david_01.dat| & 87 & 406 & 6 & 00:00:00.05 \\
    \verb|david_02.dat| & 87 & 406 & 9 & 00:00:00.05 \\
    \verb|games120_01.dat| & 120 & 638 & 7 & 00:00:00.05 \\
    \verb|games120_02.dat| & 120 & 638 & 13 & 00:00:00.05 \\
    \verb|huck_01.dat| & 74 & 301 & 7 & 00:00:00.05 \\
    \verb|huck_02.dat| & 74 & 301 & 7 & 00:00:00.05 \\
    \verb|latin_square_10_01.dat| & 900 & 307350 & 1 & 00:00:00.28 \\
    \verb|latin_square_10_02.dat| & 900 & 307350 & 1 & 00:00:00.09 \\
  \end{tabular}
  \caption{Solutions for color benchmarks (part 2)}
\end{table}

\begin{table}\footnotesize\center
  \begin{tabular}{y{3.6cm}x{1cm}x{1.5cm}x{1.5cm}y{1.5cm}}
    \multicolumn{1}{c}{\textbf{Dat File}} &
    \multicolumn{1}{c}{\textbf{n}} &
    \multicolumn{1}{c}{\textbf{m}} &
    \multicolumn{1}{c}{\textbf{Solution}} &
    \multicolumn{1}{c}{\textbf{Time}} \\
    \verb|le450_15a_01.dat| & 450 & 8168 & 3 & 00:00:00.06 \\
    \verb|le450_15a_02.dat| & 450 & 8168 & 3 & 00:00:00.05 \\
    \verb|le450_15b_01.dat| & 450 & 8169 & 2 & 00:00:00.05 \\
    \verb|le450_15b_02.dat| & 450 & 8169 & 5 & 00:00:00.05 \\
    \verb|le450_15c_01.dat| & 450 & 16680 & 2 & 00:00:00.05 \\
    \verb|le450_15c_02.dat| & 450 & 16680 & 3 & 00:00:00.05 \\
    \verb|le450_15d_01.dat| & 450 & 16750 & 2 & 00:00:00.05 \\
    \verb|le450_15d_02.dat| & 450 & 16750 & 6 & 00:00:00.05 \\
    \verb|le450_25a_01.dat| & 450 & 8260 & 3 & 00:00:00.07 \\
    \verb|le450_25a_02.dat| & 450 & 8260 & 12 & 00:00:00.05 \\
    \verb|le450_25b_01.dat| & 450 & 8263 & 6 & 00:00:00.05 \\
    \verb|le450_25b_02.dat| & 450 & 8263 & 10 & 00:00:00.05 \\
    \verb|le450_25c_01.dat| & 450 & 17343 & 3 & 00:00:00.07 \\
    \verb|le450_25c_02.dat| & 450 & 17343 & 5 & 00:00:00.05 \\
    \verb|le450_25d_01.dat| & 450 & 17425 & 3 & 00:00:00.05 \\
    \verb|le450_25d_02.dat| & 450 & 17425 & 2 & 00:00:00.05 \\
    \verb|le450_5a_01.dat| & 450 & 5714 & 1 & 00:00:00.05 \\
    \verb|le450_5a_02.dat| & 450 & 5714 & 1 & 00:00:00.05 \\
    \verb|le450_5b_01.dat| & 450 & 5734 & 1 & 00:00:00.06 \\
    \verb|le450_5b_02.dat| & 450 & 5734 & 2 & 00:00:00.05 \\
    \verb|le450_5c_01.dat| & 450 & 9803 & 1 & 00:00:00.05 \\
    \verb|le450_5c_02.dat| & 450 & 9803 & 1 & 00:00:00.05 \\
    \verb|le450_5d_01.dat| & 450 & 9757 & 1 & 00:00:00.05 \\
    \verb|le450_5d_02.dat| & 450 & 9757 & 1 & 00:00:00.05 \\
    \verb|miles1000_01.dat| & 128 & 3216 & 3 & 00:00:00.05 \\
    \verb|miles1000_02.dat| & 128 & 3216 & 5 & 00:00:00.05 \\
    \verb|miles1500_01.dat| & 128 & 5198 & 2 & 00:00:00.05 \\
    \verb|miles1500_02.dat| & 128 & 5198 & 3 & 00:00:00.05 \\
    \verb|miles500_01.dat| & 128 & 1170 & 7 & 00:00:00.05 \\
    \verb|miles500_02.dat| & 128 & 1170 & 10 & 00:00:00.05 \\
    \verb|miles750_01.dat| & 128 & 2113 & 4 & 00:00:00.05 \\
    \verb|miles750_02.dat| & 128 & 2113 & 6 & 00:00:00.05 \\
    \verb|mug100_1_01.dat| & 100 & 166 & 11 & 00:00:00.05 \\
    \verb|mug100_1_02.dat| & 100 & 166 & 18 & 00:00:00.05 \\
    \verb|mug100_25_01.dat| & 100 & 166 & 15 & 00:00:00.05 \\
    \verb|mug100_25_02.dat| & 100 & 166 & 21 & 00:00:00.05 \\
    \verb|mug88_1_01.dat| & 88 & 146 & 9 & 00:00:00.05 \\
    \verb|mug88_1_02.dat| & 88 & 146 & 20 & 00:00:00.05 \\
    \verb|mug88_25_01.dat| & 88 & 146 & 7 & 00:00:00.05 \\
    \verb|mug88_25_02.dat| & 88 & 146 & 19 & 00:00:00.05 \\
    \verb|myciel3_01.dat| & 11 & 20 & 2 & 00:00:00.05 \\
    \verb|myciel3_02.dat| & 11 & 20 & 3 & 00:00:00.05 \\
    \verb|myciel4_01.dat| & 23 & 71 & 1 & 00:00:00.05 \\
    \verb|myciel4_02.dat| & 23 & 71 & 1 & 00:00:00.05 \\
    \verb|myciel5_01.dat| & 47 & 236 & 1 & 00:00:00.05 \\
    \verb|myciel5_02.dat| & 47 & 236 & 1 & 00:00:00.05 \\
    \verb|myciel6_01.dat| & 95 & 755 & 1 & 00:00:00.05 \\
    \verb|myciel6_02.dat| & 95 & 755 & 1 & 00:00:00.05 \\
    \verb|myciel7_01.dat| & 191 & 2360 & 1 & 00:00:00.05 \\
    \verb|myciel7_02.dat| & 191 & 2360 & 1 & 00:00:00.05 \\
  \end{tabular}
  \caption{Solutions for color benchmarks (part 3)}
\end{table}

\begin{table}\footnotesize\center
  \begin{tabular}{y{3.6cm}x{1cm}x{1.5cm}x{1.5cm}y{1.5cm}}
    \multicolumn{1}{c}{\textbf{Dat File}} &
    \multicolumn{1}{c}{\textbf{n}} &
    \multicolumn{1}{c}{\textbf{m}} &
    \multicolumn{1}{c}{\textbf{Solution}} &
    \multicolumn{1}{c}{\textbf{Time}} \\
    \verb|qg.order100_01.dat| & 10000 & 990000 & 97 & 00:00:00.26 \\
    \verb|qg.order100_02.dat| & 10000 & 990000 & 98 & 00:00:00.32 \\
    \verb|qg.order30_01.dat| & 900 & 26100 & 30 & 00:00:00.08 \\
    \verb|qg.order30_02.dat| & 900 & 26100 & 29 & 00:00:00.06 \\
    \verb|qg.order40_01.dat| & 1600 & 62400 & 40 & 00:00:00.09 \\
    \verb|qg.order40_02.dat| & 1600 & 62400 & 39 & 00:00:00.06 \\
    \verb|qg.order60_01.dat| & 3600 & 212400 & 59 & 00:00:00.09 \\
    \verb|qg.order60_02.dat| & 3600 & 212400 & 58 & 00:00:00.08 \\
    \verb|queen10_10_01.dat| & 100 & 1470 & 8 & 00:00:00.06 \\
    \verb|queen10_10_02.dat| & 100 & 1470 & 11 & 00:00:00.05 \\
    \verb|queen11_11_01.dat| & 121 & 1980 & 8 & 00:00:00.05 \\
    \verb|queen11_11_02.dat| & 121 & 1980 & 8 & 00:00:00.05 \\
    \verb|queen12_12_01.dat| & 144 & 2596 & 6 & 00:00:00.05 \\
    \verb|queen12_12_02.dat| & 144 & 2596 & 9 & 00:00:00.05 \\
    \verb|queen13_13_01.dat| & 169 & 3328 & 12 & 00:00:00.08 \\
    \verb|queen13_13_02.dat| & 169 & 3328 & 4 & 00:00:00.05 \\
    \verb|queen14_14_01.dat| & 196 & 4186 & 9 & 00:00:00.05 \\
    \verb|queen14_14_02.dat| & 196 & 4186 & 8 & 00:00:00.05 \\
    \verb|queen15_15_01.dat| & 225 & 5180 & 5 & 00:00:00.05 \\
    \verb|queen15_15_02.dat| & 225 & 5180 & 4 & 00:00:00.05 \\
    \verb|queen16_16_01.dat| & 256 & 6320 & 5 & 00:00:00.05 \\
    \verb|queen16_16_02.dat| & 256 & 6320 & 7 & 00:00:00.05 \\
    \verb|queen5_5_01.dat| & 25 & 160 & 7 & 00:00:00.05 \\
    \verb|queen5_5_02.dat| & 25 & 160 & 7 & 00:00:00.05 \\
    \verb|queen6_6_01.dat| & 36 & 290 & 8 & 00:00:00.05 \\
    \verb|queen6_6_02.dat| & 36 & 290 & 9 & 00:00:00.05 \\
    \verb|queen7_7_01.dat| & 49 & 476 & 11 & 00:00:00.05 \\
    \verb|queen7_7_02.dat| & 49 & 476 & 8 & 00:00:00.05 \\
    \verb|queen8_12_01.dat| & 96 & 1368 & 10 & 00:00:00.08 \\
    \verb|queen8_12_02.dat| & 96 & 1368 & 6 & 00:00:00.05 \\
    \verb|queen8_8_01.dat| & 64 & 728 & 9 & 00:00:00.07 \\
    \verb|queen8_8_02.dat| & 64 & 728 & 9 & 00:00:00.05 \\
    \verb|queen9_9_01.dat| & 81 & 1056 & 7 & 00:00:00.05 \\
    \verb|queen9_9_02.dat| & 81 & 1056 & 5 & 00:00:00.05 \\
    \verb|school1_01.dat| & 385 & 19095 & 4 & 00:00:00.06 \\
    \verb|school1_02.dat| & 385 & 19095 & 11 & 00:00:00.05 \\
    \verb|school1_nsh_01.dat| & 352 & 14612 & 4 & 00:00:00.07 \\
    \verb|school1_nsh_02.dat| & 352 & 14612 & 8 & 00:00:00.05 \\
    \verb|wap01a_01.dat| & 2368 & 110871 & 22 & 00:00:00.07 \\
    \verb|wap01a_02.dat| & 2368 & 110871 & 76 & 00:00:00.07 \\
    \verb|wap02a_01.dat| & 2464 & 111742 & 25 & 00:00:00.08 \\
    \verb|wap02a_02.dat| & 2464 & 111742 & 97 & 00:00:00.08 \\
    \verb|wap03a_01.dat| & 4730 & 286722 & 10 & 00:00:00.10 \\
    \verb|wap03a_02.dat| & 4730 & 286722 & 96 & 00:00:00.11 \\
    \verb|wap04a_01.dat| & 5231 & 294902 & 21 & 00:00:00.10 \\
    \verb|wap04a_02.dat| & 5231 & 294902 & 112 & 00:00:00.11 \\
    \verb|wap05a_01.dat| & 905 & 43081 & 16 & 00:00:00.07 \\
    \verb|wap05a_02.dat| & 905 & 43081 & 26 & 00:00:00.06 \\
    \verb|wap06a_01.dat| & 947 & 43571 & 17 & 00:00:00.07 \\
    \verb|wap06a_02.dat| & 947 & 43571 & 36 & 00:00:00.06 \\
    \verb|wap07a_01.dat| & 1809 & 103368 & 9 & 00:00:00.08 \\
    \verb|wap07a_02.dat| & 1809 & 103368 & 36 & 00:00:00.07 \\
    \verb|wap08a_01.dat| & 1870 & 104176 & 13 & 00:00:00.07 \\
    \verb|wap08a_02.dat| & 1870 & 104176 & 43 & 00:00:00.07 \\
    \verb|will199GPIA_01.dat| & 701 & 6772 & 1 & 00:00:00.05 \\
    \verb|will199GPIA_02.dat| & 701 & 6772 & 3 & 00:00:00.05 \\
  \end{tabular}
  \caption{Solutions for color benchmarks (part 4)}
\end{table}

\end{document}

